Results_paper1

### 2019-04-12 Paper1_results.Rmd
wind+transect

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(plyr)
library(maptools)
library(sp)
library(geosphere)
library(marmap)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(fossil)
library(mapproj)
library(rgeos)

@@

# K10

@@

wind_data <- rbind(wind_3_HoutBay,wind_sitesmatched_3,wind_sitesmatched_2,wind_sitesmatched_1)
wind_data <- wind_data %>% 
  na.omit()
# save(wind_data, file = "Data_P1/wind_data.RData")

# The wind data

wind_data <- wind_data %>% 
  as.numeric(dir)

wind_data <- wind_data %>%
  mutate(date = as.Date(date)) %>%
  group_by(temp_sites, date) %>%
  summarise(mean_dir = mean(as.numeric(dir),
            mean_speed = mean(as.numeric(speed))))

save(wind_data, file = "Data/wind_daily.RData")

# load("Data/wind_daily.RData") # Loading the daily wind data for each of the sites
```

>>>>

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(plyr)
library(maptools)
library(sp)
library(geosphere)
library(marmap)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(rgeos)

@@

## K10 dataset

@@

wind_data <- rbind(wind_3_HoutBay,wind_sitesmatched_3,wind_sitesmatched_2,wind_sitesmatched_1)
wind_data <- wind_data %>% 
  na.omit()

wind_data <- wind_data %>% 
  group_by(date,hour,temp_sites) %>% 
  mutate(date = as.Date(date)) 
# write.csv(wind_data, file = "Data_P1/wind_data.csv", row.names = T)
# save(wind_data, file = "Data_P1/wind_data.RData")

# LOading the wind data
library(tidyverse)
library(circular)
wind_data <- read_csv("wind_data.csv", col_types = cols(X1 = col_number(), date = col_character(), dir = col_number(), hour = col_number(),  speed = col_number()))

wind_daily <- wind_data %>% 
  mutate(date = as.Date(date))%>%
   group_by(temp_sites, date) %>%
   summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees")),2),
             mean_speed = round(mean(speed),2))
save(wind_daily, file = "data/wind_daily.RData")

# Loading in the daily wind data
load("Data_P1/wind_daily.RData")
```
